Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-03-30 modeling-volunteer-computing-gecco.tex
Adding resources and revising

Besides, since Amazon started selling EC2 several years ago, reliable
and scalable computing resources are also available for a low price
and on demand. Recently, Google has also refurbished its offering
lowering their prices. This means that the conjunction of free or
low-cost cloud computing engines, volunteer computing systems and
untapped capability of desktop systems can be used for creating
massive, or at least potentially massive, distributed computing
experiments. These experiments can be easily created using open-source
repository sites like GitHub\footnote{\url{http://www.github.com}} and deployed automatically to Platform as
a Service (PaaS) products such as Heroku\footnote{\url{https://www.heroku.com/}} or OpenShift\footnote{\url{https://www.openshift.com/}}. 
%FERGU: luego usas el acrónimo PaaS

In general, any volunteer computing experiment will have to be made
``in the open''. The fact that somebody is giving you, basically for
free, computing resources, means that the scientist using them has to
give back. The baseline is releasing the source code used: all
volunteer computing platforms, from SETI@home on, have done it. The
opposite is probably the reason why many companies like PopularPower \cite{buyya2001compute}
have folded or others like CrowdProcess have decided to turn their
product to in-house computation: there must be a mutual relationship
of trust among the scientist and the person that is running his/her
code in the browser. As it has been mentioned in the early stages of what
was then called {\em desktop grid computing} \cite{gc:bausch}, in
fact CPU cycle selling might not make economic sense since there are
not so much demand for it and supply is quite high. However, while
potential supply is in fact huge, {\em actual} supply will depend on
the person holding it willing to actually allocate it to a particular
company selling it or a particular experiment needing it, not to
mention the fact that the experiment {\em actually} has to draw the
attention of the supplier. That is why trust is essential, and using
free software might not be enough: Openness
has to progress from open source code to open science: releasing all
data obtained in the experiment in a repository such as GitHub,
mentioned above, and even allowing real-time access to experimental data
to users.

>>>>

Besides, since Amazon started selling EC2 several years ago, reliable
and scalable computing resources are also available for a low price
and on demand. Recently, Google has also refurbished its offering
lowering their prices. This means that the conjunction of free or
low-cost cloud computing engines, volunteer computing systems and
untapped capability of desktop systems can be used for creating
massive, or at least potentially massive, distributed computing
experiments. These experiments can be easily created using open-source
repository sites like GitHub\footnote{\url{http://www.github.com}} and deployed automatically to Platform as
a Service (PaaS) sites such as
Heroku\footnote{\url{https://www.heroku.com/}} or
OpenShift\footnote{\url{https://www.openshift.com/}} or even
Infraestructure as a Service (IaaS) sites such as Microsoft's Azure.

In general, it should be a requisite for volunteer computing
experiment will have to be performed 
``in the open''. The fact that somebody is giving to you, basically for
free, computing resources, means that the scientist using them has to
give back. The baseline is releasing the source code used: all
volunteer computing platforms, from SETI@home on, have done it. The
opposite is probably the reason why many companies like PopularPower \cite{buyya2001compute}
have folded or others like CrowdProcess have decided to turn their
product to in-house computation: there must be a mutual relationship
of trust among the scientist and the person that is running his/her
code in the browser. As it has been mentioned in the early stages of what
was then called {\em desktop grid computing} \cite{gc:bausch}, in
fact CPU cycle selling might not make economic sense since there are
not so much demand for it and supply is quite high. However, while
potential supply is in fact huge, {\em actual} supply will depend on
the person holding it willing to actually allocate it to a particular
company selling it or a particular experiment needing it, not to
mention the fact that the experiment {\em actually} has to draw the
attention of the supplier. That is why trust is essential, and using
free software might not be enough: Openness
has to progress from open source code to open science: releasing all
data obtained in the experiment in a repository such as GitHub,
mentioned above, and even allowing real-time access to experimental data
to users.
